%-------------------------
% Resume in Latex
% Author : Sherwin Vishesh Jathanna
% Based off of: Jake's Resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
%sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{Lato}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sherwin V Jathanna} \\ \vspace{1pt}
     \href{https://sherwinvishesh.com}{\underline{sherwinvishesh.com}} 
   \\ \small $|$ +1 (480)810-9529 $|$ \href{mailto:sjathann@asu.edu}{\underline{sjathann@asu.edu}} $|$ 
    \href{https://linkedin.com/in/sherwinvishesh}{\underline{linkedin.com/in/sherwinvishesh}} $|$
    \href{https://github.com/sherwinvishesh}{\underline{github.com/sherwinvishesh}} $|$
\end{center}

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Soft Skills:}{ Problem-Solving, Attention to Detail, Adaptability, Communication, Collaboration} \\
    \textbf{Programming Languages:}{ Python, C, C++, Java, Perl, HTML, JavaScript, Bash, TypeScript, Solidity} \\
    \textbf{Databases:}{ MySQL, MongoDB, PostgreSQL, Database Management, Data Warehouse Management} \\
    \textbf{Tools \& Frameworks:}{ TensorFlow, PyTorch, React.js, Next.js, Node.js, Express.js, Flask, Docker, JIRA, Git} \\
    \textbf{Cloud \& Infrastructure:}{ AWS, Firebase, IT Operations, System Administration, Network Engineering, Virtualization} \\
    \textbf{Cybersecurity:}{ IT Security Fundamentals, Information Security, Data Security Methodologies, Troubleshooting} \\
    \textbf{Operating Systems: }{ Windows, Linux (Ubuntu, Kali), macOS}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Bachelor of Science in Computer Science, Minor in Business}{Aug. 2022 -- May 2026}
      \resumeItemListStart
        \resumeItem{\textbf{New American University Scholar:} Awarded \$62,000 in scholarships for academic merit.}
        \resumeItem{\textbf{Dean’s List:} Achieved Dean’s List recognition for academic excellence (Fall 2022 - Spring 2024).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Industry Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Intern}{Remote}
      {Nexus Info. Pvt. Ltd.}{Dec 2023 -- Feb 2024}
      \resumeItemListStart
        \resumeItem{Developed a dynamic restaurant management web application using the MERN stack, increasing operational efficiency by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to ensure timely delivery of high-quality web solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Online Director (On-Campus Job)}{Tempe, AZ}
      {Ira A. Fulton Schools of Engineering, Arizona State University}{Sep. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Led the development of online courses, integrating Mediasite, Zoom, and AR to improve distance learning by 45\%.}
        \resumeItem{Enhanced IT infrastructure and security for online educational platforms, ensuring compliance with university standards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Featured Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Project-Atharv} $|$ \emph{Python, Flask, APIs, Generative AI, Cloud Computing} $|$ \href{https://www.atharv.pro}{\underline{(WEBSITE)}}}{May 2024 - Present } 
          \resumeItemListStart
            \resumeItem{Launched Atharv, an AI-powered agricultural assistant, achieving 5000 users in 48 hours, improving crop disease diagnosis accuracy by 73\%.}
            \resumeItem{Collaborated with state government entities to deploy Atharv in local farming communities.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{BlockBallot} $|$ \emph{React.js, Rust, Blockchain, APIs, Information Security} $|$ \href{https://github.com/sherwinvishesh/BlockBallot}{\underline{(GITHUB)}}}{Jul 2024 } 
          \resumeItemListStart
            \resumeItem{Developed BlockBallot, a decentralized voting system on Solana, improving voter participation by 30\% and enhancing system security.}
            \resumeItem{Received honorable mention in Solana hackathon for innovation in secure voting technologies.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{StrategX} $|$ \emph{Python, Flask, AI, Machine Learning, ARIMA, Data Analysis} $|$ \href{https://github.com/sherwinvishesh/StrategX}{\underline{(GITHUB)}}}{Feb 2024 - Mar 2024 } 
          \resumeItemListStart
            \resumeItem{Built StrategX, a trading companion using AI and ML to enhance stock market decision-making by 48\%.}
            \resumeItem{Integrated data from multiple APIs to provide real-time market analysis and predictions.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{QuickAid} $|$ \emph{HTML, CSS, Node.js, Express.js, APIs, IT Security} $|$ \href{https://github.com/sherwinvishesh/QuickAid}{\underline{(GITHUB)}}}{Apr 2024 } 
          \resumeItemListStart
            \resumeItem{Developed QuickAid, an AI-powered first-aid tool that increased accuracy of initial medical responses by 40\%.}
            \resumeItem{Implemented robust data security measures to protect sensitive user information.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{myAccountant} $|$ \emph{Typescript, Python, PostgreSQL, Docker, Cloud Infrastructure} $|$ }{Dec 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Created myAccountant, an AI-powered financial advisor chatbot, improving financial decision-making accuracy by 35\%.}
            \resumeItem{Utilized cloud infrastructure for scalable deployment and efficient data processing.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Read Easy} $|$ \emph{HTML, CSS, JavaScript, Accessibility, APIs} $|$ \href{https://github.com/sherwinvishesh/Read-Easy}{\underline{(GITHUB)}}}{Jan 2024 -- Mar 2024}
          \resumeItemListStart
            \resumeItem{Developed Read Easy, a Chrome extension for enhancing online reading accessibility for individuals with dyslexia, increasing productivity by 36\%.}
            \resumeItem{Integrated with popular content platforms to provide seamless user experience.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------This is the place for hidden keywords, where it will be detected by the ATS and not by the Recruiter-----------
%\textcolor{White}{API Development, Data Analysis, Data Security Methodologies, Database Management, Enterprise Architecture, IT Operations, Machine Learning Engineering, Networking Systems, Operating Systems, Troubleshooting}

%-------------------------------------------
\end{document}
