%-------------------------
% Resume in Latex
% Author : Sherwin Vishesh Jathanna
% Tailored for: Software Engineering Intern at LinkedIn
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Sherwin Vishesh Jathanna} \\ \vspace{1pt}
     \href{https://sherwinvishesh.com}{\underline{sherwinvishesh.com}} 
   \\ \small $|$ +1 (480)810-9529 $|$ \href{mailto:sjathann@asu.edu}{\underline{sjathann@asu.edu}} $|$ 
    \href{https://linkedin.com/in/sherwinvishesh}{\underline{linkedin.com/in/sherwinvishesh}} $|$
    \href{https://github.com/sherwinvishesh}{\underline{github.com/sherwinvishesh}} $|$
     \\ 
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core Competencies:}{ Distributed Systems, Operating Systems, Cloud Computing, Data Structures, Algorithms, Software Design, Object-Oriented Programming, Multithreading, Concurrency, Scalability, Performance Optimization} \\
     \textbf{Programming Languages:}{ Python, C, C++, Java, JavaScript, TypeScript, Bash, Go, Ruby} \\
     \textbf{Frameworks and Tools:}{ Node.js, React.js, Flask, TensorFlow, PyTorch, Kubernetes, Docker, Ansible, Jenkins, Git, Perforce, SLURM, LSF} \\
     \textbf{Databases:}{ SQL (MySQL), MongoDB, Distributed Data Storage} \\
     \textbf{System-Level Debugging:}{ Unix/Shell Scripting, Linux, Configuration Automation} \\
     \textbf{Project Management:}{ Agile Development, JIRA, Trello, Notion, Asana} \\
     \textbf{Cloud and DevOps:}{ AWS, Google Cloud, CI/CD Pipelines, Microservices} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Bachelor of Science in Computer Science, Minor in Business}{Aug. 2022 -- May 2026}
      \resumeItemListStart
        \resumeItem{\textbf{New American University Scholar:} Awarded with \$62,000 worth of scholarship}
        \resumeItem{\textbf{Dean’s List (Fall 22, Spring 23, Fall 23 \& Spring 24):} Recognition for academic excellence}      
      \resumeItemListEnd
   
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Industry Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Intern}{Remote}
      {Nexus Info. Pvt. Ltd.}{Dec 2023 -- Feb 2024}
      \resumeItemListStart
        \resumeItem{Developed a scalable restaurant management application using the MERN stack, improving operational efficiency by 40\%. Applied best practices in object-oriented design, multithreading, and concurrency.}
        \resumeItem{Collaborated with a cross-functional team using Agile methodologies to deliver high-quality, unit-tested code that was reviewed and integrated continuously.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Featured Projects (Check out my github portfolio for more projects)}
    \resumeSubHeadingListStart
\resumeProjectHeading
          {\textbf{Project-Atharv} $|$ \emph{Python, Flask, APIs, Generative AI} $|$ \href{https://www.atharv.pro}{\underline{(WEBSITE)}}}{May 2024 -  Aug 2024 } 
          \resumeItemListStart
            \resumeItem{Launched Atharv, an AI-powered agricultural assistant, used by 5000 users within 48 hours. Enhanced scalability and performance through distributed computing techniques, increasing accuracy in predictions by 73\%.}
             \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{BlockBallot} $|$ \emph{React.js, Tailwind CSS, Rust, APIs} $|$ \href{https://github.com/sherwinvishesh/BlockBallot}{\underline{(GITHUB)}}}{Jul 2024 } 
          \resumeItemListStart
            \resumeItem{Engineered BlockBallot, a decentralized voting system on Solana, improving security and transparency by 30\%. Employed scalable and reliable distributed systems in the development process.}
            \resumeItemListEnd

\resumeProjectHeading
          {\textbf{QuickAid} $|$ \emph{HTML, CSS, Node.js, Express.js, APIs} $|$ \href{https://github.com/sherwinvishesh/QuickAid}{\underline{(GITHUB)}}}{Apr 2024 } 
          \resumeItemListStart
            \resumeItem{Developed QuickAid, an AI-powered first-aid tool, increasing initial medical response accuracy by 40\%. Applied core computer science concepts such as data structures and algorithms to optimize image analysis processes.}
            \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{StrategX} $|$ \emph{Python, Flask, Machine Learning, ARIMA} $|$ \href{https://github.com/sherwinvishesh/StrategX}{\underline{(GITHUB)}}}{Feb 2024 - Mar 2024 } 
          \resumeItemListStart
            \resumeItem{Designed StrategX, a web-based trading platform using machine learning for stock analysis. Implemented multi-threading to improve the decision-making process by 48\%.}
            \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Read Easy} $|$ \emph{HTML, CSS, JavaScript, APIs} $|$ \href{https://github.com/sherwinvishesh/Read-Easy}{\underline{(GITHUB)}}}{Jan 2024 -- Mar 2024}
          \resumeItemListStart
          \resumeItem{Created Read Easy, a Chrome extension for enhancing online reading accessibility. Utilized object-oriented design principles to increase productivity by 36\%.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

\section{Other Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Online Director (On-Campus Job)}{Tempe, AZ}
      {Ira A. Fulton Schools of Engineering at Arizona State University}{Sep. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Led the development and delivery of online courses using Mediasite, Zoom, and Augmented Reality, improving distance learning outcomes by 45\%. Utilized cloud computing and distributed systems to optimize content delivery.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
%-----------This is the place for hidden keywords, where it will be detected by the ATS and not by the Recruiter-----------
%\textcolor{White}{Distributed Systems, Operating Systems, Cloud Computing, Data Structures, Algorithms, Software Design, Object-Oriented Programming, Multithreading, Concurrency, Scalability, Performance Optimization, Python, C, C++, Java, Kubernetes, Docker, Ansible, CI/CD, Agile, AWS, Google Cloud}

\end{document}
